\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{enumitem}
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.25in}

\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{leftmargin=0.18in,itemsep=0pt,topsep=1pt,parsep=0pt,partopsep=0pt}
\raggedright

\newcommand{\sectiontitle}[1]{\vspace{3pt}\textbf{\large #1}\vspace{1pt}\hrule\vspace{2pt}}
\newcommand{\role}[4]{\textbf{#1} \hfill #2\\#3 \hfill #4\vspace{-2pt}}
\newcommand{\project}[2]{#1 | #2\vspace{-2pt}}

\begin{document}
\fontsize{10.4}{11.4}\selectfont

\begin{center}
{\Large \textbf{Liam Van}}\\
678-488-7259 | liamvanpj@gmail.com | Seattle, Washington | linkedin.com/in/liam-van | github.com/SpeciLiam | \href{https://liamvan.dev}{liamvan.dev}
\end{center}

\sectiontitle{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript, Java, Python, SQL, C++, C\#, PHP, C\\
\textbf{Product and UI:} React, Vite, Node.js, NestJS, Angular, mobile UX, AI-assisted systems, customer-facing products\\
\textbf{Backend / Data:} REST APIs, Spring Boot, Postgres, Supabase, MySQL, OpenSearch, data modeling, distributed caching\\
\textbf{Cloud and Ops:} Amazon Web Services, GCP, OCI, Docker, CI/CD, Grafana, Sentry, canary validation\\
\textbf{Quality:} Robot Framework, Selenium, unit testing, prompt design, technical documentation, cross-team execution

\sectiontitle{Experience}
\role{Oracle}{May 2025 - Present}{Software Engineer, GCP Integration (Oasis)}{Seattle, Washington}
\begin{itemize}
  \item Own GA readiness for OCI databases on GCP across BaseDB, ADBS, Exadata, backup, restore, and API paths.
  \item Debug cross-cloud integration issues with Oracle and GCP engineers through canary triage and release blockers.
  \item Built AI-assisted API tests for Oasis services with prompt design, Robot Framework, and auth handling.
  \item Created reusable GCloud and OCI scripts plus regression utilities for data-service release validation.
  \item Implemented Exascale Storage Vault dry-run support, improving setup validation with over 90\% unit coverage.
  \item Serve as primary release on-call, leading Sev2 investigations with logs, Grafana/T2 metrics, and alarm tuning.
  \item Document validation playbooks for product engineers supporting cross-cloud database releases.
\end{itemize}

\role{Oracle}{May 2024 - August 2024}{Software Engineer}{Redwood City, CA}
\begin{itemize}
  \item Built an LLM-powered recommendation experience for Oracle University and OCI learning content discovery.
  \item Integrated video search into Oracle University's search experience using OpenSearch indexing and retrieval pipelines.
  \item Implemented React and NestJS product surfaces for search using PHP and SQL metadata pipelines.
  \item Partnered with product stakeholders to turn Figma designs and metadata needs into shipped search surfaces.
\end{itemize}

\role{Caterpillar Inc.}{May 2023 - December 2023}{Software Engineer}{Chicago, IL}
\begin{itemize}
  \item Built Java data-processing pipelines that converted JSON to Apache Parquet and cut storage use by 30\%.
  \item Developed Java APIs and telemetry data models for equipment groups, cutting analysis time by 50\%.
  \item Implemented distributed caching for real-time search across API responses, increasing parsing speed by 1000\%.
  \item Supported API validation and release-quality checks across telemetry and search systems.
\end{itemize}

\role{Caterpillar Inc.}{May 2022 - August 2022}{Software Engineer Intern}{Chicago, IL}

\sectiontitle{Education}
\textbf{University of Georgia, School of Computing} \hfill Athens, GA\\
Bachelor of Science in Computer Science

\sectiontitle{Projects}
\project{SplitCheck}{React, Vite, Capacitor, Supabase, Postgres, AI}
\begin{itemize}
  \item Built a mobile-first receipt splitting app with diner assignment, guest claims, and Venmo/Zelle handoff.
  \item Designed Supabase Edge Functions for AI receipt parsing, share links, guest updates, payments, and exports.
  \item Added realtime host refresh with edit-safe debouncing and fallback polling for guest activity.
  \item Added privacy and launch foundations across RLS policies, receipt retention, telemetry, and store-readiness docs.
  \item Built Supabase Auth, Storage, Postgres, and Realtime paths for saved splits, receipt images, and guest activity.
  \item Added Sentry and app telemetry paths for frontend error capture and product-event tracking.
\end{itemize}

\project{Fantasy Wizard}{React, TypeScript, Spring Boot, AI, REST APIs}
\begin{itemize}
  \item Built an AI fantasy advisor for live Sleeper, ESPN, and Yahoo roster, draft, waiver, and trade decisions.
  \item Designed Spring Boot provider flows for account linking, ESPN draft hydration, caching, and provider-aware UI.
  \item Deployed the Vite frontend and Railway backend with Postgres-backed saved league/provider connections.
  \item Added tests for ESPN clients, provider adapters, draft flows, league APIs, and user/account surfaces.
  \item Built source comparison and league insight surfaces around live player, roster, matchup, and transaction context.
  \item Implemented provider capability responses so the frontend gates unsupported data surfaces accurately.
\end{itemize}

\end{document}
